### 2020-12-09 paper/localpsf.tex
literature review gah

@@

\subsection{old stuff}

The most popular existing Hessian approximation methods are based on forming a low rank approximation of the data misfit term in the Hessian, or the data misfit term preconditioned by the prior term. Either the Lanczos method or randomized SVD are used to perform the low rank approximation using only matrix-vector products. The larger the rank of the approximation, the more matrix-vector products are required. These methods suffer from a ``data predicament''---as more informative data is used in the inversion, the numerical rank of the data misfit term in the Hessian grows. The ideal scenario from a scientific perspective (highly informative data) is therefore the worst case scenario from a computational perspective (large computational cost). In our numerical results, we show that our operator approximation method can efficiently approximate the data misfit term in the Hessian in certain PDE constrained inverse problems. The method in this paper offers a \emph{data-scalable} alternative to conventional low-rank Hessian approximation methods, because the rank of the approximation is not limited by the number of matrix-vector products used to construct the approximation. High-rank approximations of an operator can be formed using a small number of matrix-vector products.

@@

>>>>

The most popular existing Hessian approximation methods are based on forming a low rank approximation of the data misfit term in the Hessian, or the data misfit term preconditioned by the prior term [CITE LOTS OF STUFF]. Either the Lanczos method or the randomized singular value decomposition are used to perform the low rank approximation using only matrix-vector products. These methods suffer from a ``data predicament''---as more informative data is used in the inversion, the numerical rank of the data misfit term in the Hessian grows, so more matrix-vector products are required to form the aforementioned low rank approximation. The ideal scenario from a scientific perspective (highly informative data) is therefore the worst case scenario from a computational perspective (large computational cost) [CITE MY DISSERTATION]. In our numerical results, we show that our operator approximation method can efficiently approximate the data misfit term in the Hessian in certain PDE constrained inverse problems. The method in this paper offers a \emph{data-scalable} alternative to conventional low-rank Hessian approximation methods, because the rank of the approximation is not limited by the number of matrix-vector products used to construct the approximation. High-rank approximations of an operator can be formed using a small number of matrix-vector products.

@@

@@

\section{old stuff}
